A weighted data representation based approach for manifold learning

### 2018-11-05 DimReduction/Lle/Documentation/Article_lle.tex
Adding results section to Lle documentation

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{algorithm2e}

@@

\begin{abstract}
    We present a detailed implementation of the local linear embeding algorithm
    from both a theoretical and practical approximation. In this work the
    dimensionality reduction is achieved by a two step procedure. First a
    weighted data representation based in $K$ nearest neighbors is calculated,
    and then a minimization of distance between the data representation and a
    low dimensionality configuration is conducted. Finally the resulting
    algorithm is tested on 3-dimensional manifolds.
\end{abstract}

@@

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{algorithm2e}
\usepackage{float}

@@

\begin{abstract}
    This work presents a detailed implementation of the local linear embeding algorithm
    from both a theoretical and practical approximation. In this work the
    dimensionality reduction is achieved by a two step procedure. First a
    weighted data representation based in $K$ nearest neighbors is calculated,
    and then a minimization of distance between the data representation and a
    low dimensionality configuration is conducted. Finally the resulting
    algorithm is tested on 3-dimensional manifolds.
\end{abstract}

@@

The algorithm described in the previous secction was tested with 2 manifolds in
a 3 dimensional space. Figure \ref{swiss} shows a swiss roll dataset that
represents the manifold that the method is going to reduce, the resulting
2 dimensional dataset is shown in Figure \ref{swiss_res}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{images/swiss_roll.png}
    \caption{Swiss roll dataset}
    \label{swiss}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{images/swiss_roll_result.png}
    \caption{Swiss roll dataset reduced}
    \label{swiss_res}
\end{figure}

Finally in Figure \ref{sphere} a second manifold in form of a 3 dimensional
sphere is shown, the result of the method is shown in Figure \ref{sphere_res}
as a 2 dimensional configuration of points.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{images/sphere.png}
    \caption{Sphere dataset}
    \label{sphere}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{images/sphere_result.png}
    \caption{Sphere dataset reduced}
    \label{sphere_res}
\end{figure}

@@

In this work
